---
title: "Creating the ``r params$package_name`` R package"
author: "Siddhi Apraj"
date: "25 Feb 2023"
knit: litr::render
output: litr::litr_html_document
params:
  package_name: "youDrawItEducate" # <-- change this to your package name
  package_parent_dir: "." # <-- relative to this file's location
---

<!-- This Rmd file contains all the code needed to define an R package.  Press "Knit" in RStudio or more generally run `litr::render("name-of-this-file.Rmd")` to generate the R package.  Remember that when you want to modify anything about the R package, you should modify this document rather than the package that is outputted.
-->

## Package setup

We start by specifying the information needed in the DESCRIPTION file of the R package.

```{r package-setup, message=FALSE, results='hide'}
usethis::create_package(
  path = ".",
  fields = list(
    Package = params$package_name,
    Version = "0.0.0.9000",
    Title = "A Package That Allows to Experiment with Regression",
    Description = "This package allows to conduct experiment with Statistics Regression.",
    `Authors@R` = person(
      given = "Siddhi",
      family = "Apraj",
      email = "siddhiapraj@gmail.com",
      role = c("aut", "cre")
      )
  )
)
usethis::use_mit_license(copyright_holder = "F. Last")
```

## Now to the package itself



```{r}
#' You draw it package App UI
#' 
ydtUI <- function(id) {

  navbarPage(
    "Can 'You Draw It'?",

    tabPanel(
        title = "Example: Eye Fitting Straight Lines in the Modern Era",
        tags$head(
        tags$link(rel = "stylesheet", type = "text/css", href = "css/d3.css")
        ),
        fluidRow(
        column(
            width = 12,
            helpText(h4("Use your mouse to fill in the trend in the yellow box region")),
            d3Output(NS(id,"shinydrawr"), height = "500px"),
            br(),
            textOutput(NS(id,"tip")),
            actionButton(NS(id,"reset"), "Reset")
        )

        )
    )
  )
}
```

### Define a function

Let's define a function for our R package:

```{r}
#' You draw it package App
#' 
#' @export 
library(shiny)
library(shinyjs)
library(shinyBS)
library(r2d3)
library(tidyverse)
library(purrr)
library(gridSVG)
library(lubridate)
library(readxl)
library(renv)

ydtApp <- function(...) {
    ui <- fluidPage (ydtUI("hist1")
    )
    
    server <- function(input, output, session) {
        ydtServer("hist1")
    }
    
    shinyApp(ui, server,...)
}
```

Code chunks whose first line starts with `#'` are added to the package.

We can try running it.

```{r}
ydtApp()
```

That code chunk does not start with `#'`, so it is not added to the package.

Let's write some tests to make sure the function behaves as desired:

```{r}
testthat::test_that("say_hello works", {
  testthat::expect_silent(ydtApp())
})
```

Code chunks that have one or more lines starting with `test_that(` (or `testthat::test_that(`) are added to the package as tests.

## Documenting the package and building

We finish by running commands that will document, build, and install the package.  It may also be a good idea to check the package from within this file.

```{r}
litr::document() # <-- use instead of devtools::document()
# devtools::build()
# devtools::install()
# devtools::check(document = FALSE)
```


